---
title: "My second dashboard"
author: "Priyanka Govindarajan"
date: "2023-11-04"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(shiny)
library(dplyr)
library(plotly)
library(ggplot2)
library(colourpicker)
# load data in 'global' chunk so it can be shared
# by all users of the dashboard
library(datasets)
data(faithful)

data <- read.csv("BankChurners.csv")
Categorical.Variables = c("Gender", "Education_Level", "Marital_Status")
Numeric.Variables = c("Customer_Age", "Total_Trans_Ct", "Credit_Limit")

diamonds_data=diamonds[1:20,]
```
Faithful Viz
===
Column {.sidebar}
--------------------------------------------------

Waiting time between eruptions and the duration of the eruption
for the Old Faithful geyser in Yellowstone National Park,
Wyoming, USA.

```{r}
selectInput(
  "n_breaks", label = "Number of bins:",
  choices = c(10, 20, 35, 50), selected = 20
)

sliderInput(
  "bw_adjust", label = "Bandwidth adjustment:",
  min = 0.2, max = 2, value = 1, step = 0.2
)
```
Column
--------------------------------------------------
### Geyser Eruption Duration

```{r}
renderPlot({
  erpt = faithful$eruptions
  hist(
    erpt, probability = TRUE, breaks = as.integer(input$n_breaks),
    xlab = "Duration (minutes)", main = "Geyser Eruption Duration",
    col = 'black', border = 'white'
  )
  
  dens = density(erpt, adjust = input$bw_adjust)
  lines(dens, col = "purple", lwd = 2)
})
```


Bank Viz
===
Column {.sidebar data-width=200}
-----------------------------------------------------------------------

```{r}

#Dropdown
#selectInput("categorical_variable", label = "Select Categorical Variable:", choices = Categorical.Variables)

#selectInput("numeric_variable", label = "Select Numeric Variable:", choices = Numeric.Variables)

#Checkbox
checkboxGroupInput("categorical_variable", label = "Select Categorical Variable:", choices = Categorical.Variables, selected = "Gender")

checkboxGroupInput("numeric_variable", label = "Select Numeric Variable:", choices = Numeric.Variables, selected = "Customer_Age")


```
Column {data-width=400,}
-----------------------------------------------------------------------

### Chart A

```{r}
renderPlotly({
   plot_ly(data,
              x = ~data[[input$numeric_variable]],
              color = ~data[[input$categorical_variable]],
              colors = "Paired",
              type = "box") %>%
  layout(title = "",
         xaxis = list(title = "" ,
                      zeroline = FALSE))
})
```
Column {data-width=400}
-----------------------------------------------------------------------

### Chart B

```{r}
renderPlotly({
  data %>%
    count(var = data[[input$categorical_variable]], name = "count") %>%
    plot_ly( x = ~var, y = ~ count, type = "bar", marker = list(color = '#008ae6',
                           line = list(color = '#008ae6', width = 2)), hoverinfo = "x+y") %>%
    add_text(text = ~paste0( " (",   scales::percent(count/sum(count)),")"), 
           textposition = "bottom", 
           textfont = list(size = 12, color = "white"), 
           showlegend = FALSE) %>%
    layout(xaxis = list(title = ""), yaxis = list(title = ""))
    
})
```

Diamonds Viz
===
Column {data-width=400, .tabset}
-----------------------------------------------------------------------

### Chart A

```{r}
diaviz <- ggplot(data = diamonds_data, aes(x = color, y = depth, color = cut, shape = clarity)) + geom_point(size = 3)

diaviz %>% 
  ggplotly()
```

### Chart B

```{r}
radioButtons(inputId = "plot_type" , label = "Select the plot", choices = c("scatter", "bar", "hist" ))
renderPlot({
    if (input$plot_type == "scatter") {
      ggplot(diamonds_data, aes(cut, price)) + geom_point()
    } else if (input$plot_type == "bar") {
      ggplot(diamonds_data, aes(x=cut, y=price, fill=cut)) + geom_bar(stat="identity")
    }
      else if (input$plot_type == "hist") {
      ggplot(diamonds_data, aes(price)) + geom_histogram()
    }
  })

```
### Chart C

```{r}
colourInput("col", "Choose colour", "red")
renderPlot({
  ggplot(diamonds_data, aes(price)) + geom_histogram(fill = input$col) 
  })

```

Page 3 {data-navmenu="Menu A" data-navmenu-icon="fa-bookmark"}
=====================================


Page 4 {data-navmenu="Menu A"}
=====================================  


Page 5 {data-navmenu="Menu B" data-navmenu="fa-cog"}
=====================================


Page 6 {data-navmenu="Menu B"}
==========================================

Page 7
===================================== 

You can link to a dashboard page with the following syntax:

[Page 8]

The second syntax is used when you want a custom name for the link 
(rather than just using the page title).

### Chart A
    
```{r}
```

Page 8
=====================================     

### Chart B
    
```{r}
```
=====================================  
