---
title: "my first dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: column #change this to row
    vertical_layout: fill #fill/scroll
    runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(dygraphs)
```
Page 1
===
Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Visualizations {data-icon="fa-signal"}
===
Column
-----------------------------------------------------------------------

### Chart B {data-height=200}

- one
- two 
- three

### Chart C 
Text board

```{r}

```

Tables {data-icon="fa-table"}
===
Column {data-width=350}
-----------------------------------------------------------------------

### Chart D

```{r}

```

### Chart E

```{r}

```

### Chart F

```{r}

```

Page 4 {data-orientation=rows}
===
Row {data-height=650}
-------------------------------------
    
### Chart 1
    
```{r}

```
   
Row {data-height=350}
-------------------------------------
    
### Chart 2
    
```{r}

```
    
### Chart 3

```{r}

```

Page 5
===
Column {data-width=600}
-------------------------------------
    
### Chart 1
    
```{r}

```
   
Column {data-width=400}
-------------------------------------
   
### Chart 2

```{r}

```   
 
### Chart 3
    
```{r}

```
Page 6 {data-icon="fa-hashtag"}
===
Column 
-------------------------------------
    
### Chart 1
    
```{r}

```
   
Column {data-width=400, .tabset}
-------------------------------------
   
### Chart 2

```{r}

```   
 
### Chart 3
    
```{r}

```
Page 7 {data-orientation=rows}
===
Row 
-------------------------------------
    
### Chart 1
    
```{r}

```
   
Row {.tabset .tabset-fade}
-------------------------------------
   
### Chart 2

```{r}

```   
 
### Chart 3
    
```{r}

```

Page 8 {data-orientation=rows}
===
Row
-----------------------------------------------------------------------

### Articles per Day

```{r}
valueBox(45, icon = "fa-pencil", href="#details")
```

### Comments per Day

```{r}
valueBox(126, icon = "fa-comments")
```

### Spam per Day

```{r}
spam <- 5
valueBox(spam, 
         icon = "fa-trash",
         color = ifelse(spam > 10, "warning", "primary"))
```

Page 9 {data-orientation=rows}
===
Row {data-height=350}
-----------------------------------------------------------------------

### Contact Rate

```{r}
gauge(90, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Average Rating 

```{r}
gauge(37.4, min = 0, max = 50, gaugeSectors(
  success = c(41, 50), warning = c(21, 40), danger = c(0, 20)
))
```

### Cancellations

```{r}
gauge(7, min = 0, max = 10, gaugeSectors(
  success = c(0, 2), warning = c(3, 6), danger = c(7, 10)
))
```

Page 10
===
Column
-------------------------------------
    
### Chart 1 {data-height=600}
    
```{r}

```
   
### Chart 2 {data-height=200}

```{r}

```   
 
### Chart 3 {data-height=200}
    
```{r}

```

Page 11 {data-orientation=rows}
===
Row 
-------------------------------------
    
### Basic bar plot
    
```{r}
data(diamonds)
diamonds %>% 
  ggplot(aes(x = cut, y = mean(price), fill = cut)) +
  geom_bar(stat = "identity") +
  
  ggtitle("Basic Bar Plot") +
  xlab("CUT") +
  ylab("price") +
  theme_bw() +
  theme(axis.text.x = element_text(face = 'bold', size = 10),
        axis.text.y = element_text(face = 'bold', size = 10))
```
   
Row {.tabset .tabset-fade}
-------------------------------------
   
### Stacked Bar plot

```{r}
diamonds %>% 
  ggplot(aes(x = cut, fill = clarity)) + # removed y argument and value
  geom_bar() +
  ggtitle("Stacked Bar Plot") +
  xlab("CUT") +
  ylab("COUNT") +
  theme_bw() +
  theme(axis.text.x = element_text(face = 'bold', size = 10),
        axis.text.y = element_text(face = 'bold', size = 10))
```   
 
### Density plot
    
```{r}
ggplot(diamonds) +
  geom_density(aes(x = price, 
                   fill = cut), alpha = 0.7)+
  
  ggtitle("Density Plot") +
  xlab("price") +
  ylab("Density") +
  theme_bw() +
  theme(axis.text.x = element_text(face = 'bold', size = 10),
        axis.text.y = element_text(face = 'bold', size = 10))
```

Page 12 {data-orientation=rows}
===
Row
-----------------------------------------------------------------------

### Articles per Day

```{r}
valueBox(45, icon = "fa-pencil", href="#details")
```

### Comments per Day

```{r}
valueBox(126, icon = "fa-comments")
```

### Spam per Day

```{r}
spam <- 5
valueBox(spam, 
         icon = "fa-trash",
         color = ifelse(spam > 10, "warning", "primary"))
```

Row {.tabset .tabset-fade}
-------------------------------------

### Basic bar plot
    
```{r}
data(diamonds)
diamonds %>% 
  ggplot(aes(x = cut, y = mean(price), fill = cut)) +
  geom_bar(stat = "identity") +
  
  ggtitle("Basic Bar Plot") +
  xlab("CUT") +
  ylab("price") +
  theme_bw() +
  theme(axis.text.x = element_text(face = 'bold', size = 10),
        axis.text.y = element_text(face = 'bold', size = 10))
```
   
### Stacked Bar plot

```{r}
diamonds %>% 
  ggplot(aes(x = cut, fill = clarity)) + # removed y argument and value
  geom_bar() +
  ggtitle("Stacked Bar Plot") +
  xlab("CUT") +
  ylab("COUNT") +
  theme_bw() +
  theme(axis.text.x = element_text(face = 'bold', size = 10),
        axis.text.y = element_text(face = 'bold', size = 10))
```   
 
### Density plot
    
```{r}
ggplot(diamonds) +
  geom_density(aes(x = price, 
                   fill = cut), alpha = 0.7)+
  
  ggtitle("Density Plot") +
  xlab("price") +
  ylab("Density") +
  theme_bw() +
  theme(axis.text.x = element_text(face = 'bold', size = 10),
        axis.text.y = element_text(face = 'bold', size = 10))
```

Page13
===
Row {data-height=600}
-------------------------------------

### All Lung Deaths

```{r}
dygraph(ldeaths)
```
Row {data-height=400}
-------------------------------------

### Male Deaths

```{r}
dygraph(mdeaths)
```
### About dygraphs

This example makes use of the dygraphs R package. The dygraphs
package provides rich facilities for charting time-series data 
in R. You can use dygraphs at the R console, within R Markdown
documents, and within Shiny applications.